\addstarredchapterc{Abstract}
\chapter*{Abstract}
\begin{abstract}
  The ability to provide uninterrupted connectivity and employ ``cloud-first'' architecture for the Order Management System and Event Industries has become a major focus of digital disruption in both of these spaces. However, due to the nature of their temporary events (i.e., Cultural Festivals) and associated ad-hoc network infrastructures, they are considered extremely hostile. This is largely due to extreme latency spikes, localized Radio Frequency Interference (RFI), and complete loss of connectivity. As such, in environments where there are numerous intensity points (e.g., POS terminals, Kiosks, etc.) and the use of Synchronous HTTP Polling in Traditional Point-of-Sale (POS) Systems will often cause problems referred to as the ``Two Generals Problem'' which results in extreme Data Desynchronization, Phantom Orders and Financial Discrepancies.
  
  This dissertation describes the design, development and experimental validation of an Order Management System (OMS) that provides a high-performance capability for managing orders in a localized environment. The OMS is specifically designed to be capable of managing orders in hostile networking environments. An important architectural component of this system utilizes an Optimized, Event Driven Internal Topology built upon the MERN technology stack (MongoDB, Express.js, React, Node.js). A significant benefit of utilizing this type of internal topology is that it allows for a decoupling of the Operational Interface from External Cloud Dependencies. To further improve its performance capabilities in hostile networking environments, the Proposed Architecture replaces Synchronous HTTP Polling with Full-Duplex WebSocket Connections and uses Resilient React Based Virtual DOM Interfaces and Offline-First Caching to ensure Deterministic State Synchronization Across Isolated Operational Nodes (Cashiers, Kitchen Staff, Administrative Hubs). Additionally, strict security boundaries are utilized and enforced using JWTs and Zero Trust RBAC for Access Control.

  In order to empirically evaluate the performance characteristics of the proposed architecture, rigorous evaluations were performed. These evaluations included High-Intensity Stress Testing (Validated Stability at 1.58 Million Concurrent Transactions) and Chaos Engineering Simulations that demonstrated a Severe Failure Recovery Time Objective (RTO) of 310 Milliseconds. Laboratory measurements made during the evaluations were subsequently validated through extensive field deployments over the course of seven days with massive Burst Traffic. Telemetry collected during the field deployment validated that Asynchronous Event Loop Architectures significantly reduce Bandwidth Payload and eliminate Connection-Based Degradation when deployed in Hostile Networking Environments.
  
  \vspace{1em}
  \textbf{Keywords:} Order Management System, Event-Driven Architecture, WebSockets, Local-First Topology, Ad-hoc Networks, High-Throughput Computing, Real-Time Synchronization.
\end{abstract}
